Parameter-efficient fine-tuning (PEFT) reduces the number of trainable parameters, but efficient adaptation also depends on which examples drive training. Existing data selectors usually estimate one task-conditioned value per example and reuse the resulting subset across PEFT methods. This paper studies a structural source of mismatch in that practice: PEFT methods expose different trainable subspaces, so the same example can have different utility under LoRA, adapters, and (IA)$^3$.

We introduce PCU-Select (PEFT-Conditional Utility), a PEFT-conditioned data selector that predicts sample utility from three conditions: the candidate example, a target-task sketch, and a structured PEFT configuration. PCU-Select aligns sample and task gradients on 24 intervention sites, reweights those sites by the target PEFT, corrects the proxy with short-horizon high-fidelity labels, and selects a coverage-aware subset with uncertainty penalties. Across four tasks, five seen PEFT configurations, and three target-training seeds, PCU-Select improves the 10\% budget average---an arithmetic average of task-native percentage metrics used only as a compact summary and reported with per-task results---over random selection by 2.89 points and over RDS+ by 0.74 points. It reaches downstream performance statistically equivalent to a per-PEFT LESS reimplementation on these seen configurations (paired difference $0.04$ points, 95\% CI $[-0.26, 0.33]$, Wilcoxon $p=0.70$, and two one-sided tests establishing equivalence within a $\pm1.0$-point margin, $p<0.01$).

PCU-Select's main advantage over LESS is amortization, not a per-target performance win. Because its supervision is computed once and reused, the offline cost amortizes after about 1.6 target PEFT configurations relative to per-PEFT LESS gradient recomputation, though cheaper PEFT-agnostic selectors remain preferable when few targets are trained. These claims hold for the fixed Llama-2-7B backbone family and the seen PEFT registry; extrapolated configurations and unseen PEFT families require calibration. Ablations confirm that PEFT encoding, task sketches, multi-fidelity supervision, and coverage-aware quotas all contribute to performance.
