\section{Related Work}

Our work is related to two broad lines of research: data-efficient fine-tuning, which aims to reduce the number of training examples, and parameter-efficient fine-tuning, which aims to reduce the number of trainable parameters. We discuss both areas and then position our work at their intersection.

\subsection{Data-Efficient Fine-Tuning}

\paragraph{Quality-, complexity-, and diversity-based selection.}
A central finding in instruction tuning is that high-quality data can be more valuable than large quantities of noisy data. LIMA fine-tunes a 65B LLaMA model on only 1,000 carefully curated examples and obtains strong alignment behavior without RLHF \cite{zhou2023lima}, demonstrating that much of the model's knowledge is already acquired during pre-training and that supervised fine-tuning can act mainly as a format- and behavior-alignment stage. Following this observation, many studies attempt to characterize what makes instruction data useful. AlpaGasus uses a stronger LLM to filter low-quality Alpaca examples and trains stronger models with substantially fewer examples \cite{chen2024alpagasus}. InsTag introduces fine-grained semantic tags to measure instruction diversity and complexity, and selects examples that cover rich intent patterns \cite{lu2023instag}. DEITA studies automatic data selection along quality, complexity, and diversity dimensions and shows that a small selected subset can compete with much larger alignment datasets \cite{liu2024deita}. Other work focuses on preserving diversity explicitly, for example through quality-diversity trade-offs \cite{bukharin2023diversity}, determinantal point processes or log-determinant diversity measures \cite{wang2024diversity}, or partition-aware mini-batch construction as in CommonIT \cite{rao2024commonit}. These methods improve data efficiency, but they generally treat data quality or diversity as global properties of examples rather than as quantities conditioned on the target PEFT mechanism.

\paragraph{Model-assisted data selection.}
Another line of work relies on external models to score or filter instruction examples. Strong LLMs can act as judges for instruction-response quality, as in AlpaGasus \cite{chen2024alpagasus}. Cherry LLM proposes the instruction-following difficulty (IFD) score to identify examples for which the instruction context substantially improves the model's ability to generate the response \cite{li2023cherry}. Because using strong LLMs for large-scale scoring can be expensive, several studies use smaller proxy models. Superfiltering shows that weak models can rank examples similarly to stronger models under certain difficulty metrics \cite{wang2024superfiltering}. SmallToLarge (S2L) summarizes training trajectories from smaller models to select data for larger target models, substantially reducing selection cost \cite{yang2024smalltolarge}. MoDS selects instruction data according to quality, coverage, and necessity relative to a target model \cite{du2023mods}. These approaches recognize that data value can be model-dependent, but they mainly study dependence on model size, model family, or learning dynamics, not dependence on the trainable subspace exposed by different PEFT methods.

\paragraph{Influence- and gradient-based selection.}
Influence-based methods attempt to estimate how individual training examples affect validation performance. Classical influence functions approximate the effect of removing or upweighting a training example through second-order information \cite{koh2017understanding}, while TracIn estimates influence through gradient similarities accumulated along training trajectories \cite{pruthi2020tracin}. For modern LLMs, exact influence estimation is usually infeasible, so recent methods develop scalable approximations. LESS constructs a reusable low-dimensional gradient datastore and selects instruction examples whose gradients align with those of a small target development set \cite{xia2024less}. DataInf proposes an efficient influence approximation particularly suited to LoRA-tuned generative models \cite{kwon2023datainf}. SHED and related Shapley-value methods seek to assign credit to data points while accounting for redundancy or interaction among examples \cite{he2024shed, ghorbani2019datashapley}. Compared with quality- or embedding-based selection, gradient-based methods more directly capture optimization relevance. However, they are often instantiated with a single adaptation setup and then treated as broadly transferable. Our work asks whether such transfer remains valid when the target PEFT method changes.

\paragraph{Dynamic and curriculum-based selection.}
Instead of selecting a fixed subset before training, dynamic data selection methods adapt the training distribution over time. Active-learning methods such as AcTune query uncertain examples while using confident examples for self-training \cite{yu2021actune}. Skill-It organizes data into skills and learns online sampling schedules based on skill dependencies and current validation loss \cite{chen2023skillit}. GREATS and related gradient-based curriculum methods estimate the immediate effect of candidate examples on validation loss and select examples during training \cite{zhao2024greats}. Self-guided curriculum methods also let LLMs generate or schedule their own learning data \cite{zhang2024citing}. These methods show that data value can change during training, but they do not directly address how the definition of value changes when different PEFT modules are optimized.

\subsection{Parameter-Efficient Fine-Tuning}

PEFT methods reduce adaptation cost by updating only a small subset of parameters while keeping the backbone largely frozen. Adapter-based methods insert small trainable bottleneck modules into Transformer layers and keep original model parameters fixed \cite{houlsby2019adapters, pfeiffer2020adapterfusion}. Prompt tuning and prefix tuning instead optimize continuous prompt vectors or prefix key-value states while leaving the model weights unchanged \cite{li2021prefixtuning, lester2021prompttuning}. LoRA assumes that downstream weight updates are approximately low-rank and injects trainable rank-decomposition matrices into selected linear layers \cite{hu2022lora}. QLoRA combines quantized backbones with LoRA adapters to further reduce memory requirements during fine-tuning \cite{dettmers2023qlora}. Sparse and multiplicative methods update even fewer parameters: BitFit tunes only bias terms \cite{zaken2022bitfit}, while (IA)$^3$ learns vectors that rescale keys, values, and feed-forward activations \cite{liu2022ia3}.

Although these methods are grouped under the common PEFT umbrella, they differ substantially in adaptation geometry. LoRA learns additive low-rank matrix updates, adapters add residual nonlinear transformations, prompt-based methods modify the effective context, and (IA)$^3$ performs multiplicative activation gating. These differences imply different capacity, update locations, optimizer states, and gradient representations. Most PEFT studies compare final performance, trainable parameter counts, memory cost, or inference overhead under fixed data. In contrast, our work focuses on a complementary question: when the data pool is fixed, do different PEFT methods assign the same value to each training example?

\subsection{Joint Data- and Parameter-Efficient Adaptation}

Data-efficient fine-tuning and PEFT address two sides of the same efficiency problem. Data selection reduces the number of examples and training steps, while PEFT reduces the number of parameters and optimizer states. Combining them is therefore essential for economical LLM adaptation. However, most existing work studies the two dimensions separately. Data-efficient methods often assume that selected examples are generally useful across adaptation methods; PEFT methods usually assume that the training data is fixed or already curated. A few works move closer to the intersection. DataInf explicitly studies influence estimation for LoRA-tuned models \cite{kwon2023datainf}, and LESS uses low-dimensional gradient representations that can be transferred across models \cite{xia2024less}. Recent geometry-aware targeted selection methods further suggest that PEFT optimization can have nontrivial subspace structure \cite{min2026gist}. Nevertheless, the question of cross-PEFT transfer remains underexplored: a subset selected using LoRA gradients may not be the subset that best trains adapters or (IA)$^3$.

Our work fills this gap by treating the target PEFT method as part of the data selection condition. Instead of asking whether an example is useful in a PEFT-agnostic sense, we ask whether it is useful under the specific trainable parameter space that will be optimized. This perspective reframes data value as a conditional quantity and motivates PEFT-aware data-value modeling for joint data- and parameter-efficient LLM adaptation.
