\section{Experiments}
\label{sec:experiments}

The evaluation tests three claims. PCU-Select should match per-PEFT influence selection on downstream quality, amortize selection cost across a PEFT registry, and support new configurations according to their structural distance from the training registry.

\subsection{Setup}

We evaluate on GSM8K, HumanEval, MMLU, and TyDiQA~\cite{cobbe2021gsm8k,chen2021humaneval,hendrycks2021mmlu,clark2020tydiqa}. We use each task's native metric: exact match, Pass@1, accuracy, or F1. The candidate pool contains 300K mixed instruction examples, and every selector chooses 10\%. Each method uses the same target backbone, PEFT recipe, number of steps, and evaluation protocol. Only the selected subset changes. For the main table, we vary target-training seeds 0, 1, and 2 while fixing selector, scorer, sketch, and pool state at seed 0. Appendix Table~\ref{tab:appendix-peft-registry} lists the full 17-configuration registry.

This protocol isolates selection quality from optimization noise. Matched seeds give every selector the same target-training randomness. Cell-wise differences therefore reflect the subset instead of initialization or data order. Because we fix the sketch and selector state, the intervals describe variation across evaluated PEFT--task cells. They do not capture uncertainty from retraining the scorer or resampling the pool.

The five seen configurations cover attention and MLP LoRA, (IA)$^3$, and adapters. Held-out tests vary rank, placement, learning rate, and family. We compare Random, RDS+, and two gradient baselines, Influence and LESS; Appendix~\ref{sec:appendix-baselines} gives full specifications. \textbf{RDS+} ranks frozen external semantic embeddings against the task-sketch mean and ignores the PEFT configuration. \textbf{Influence} uses projected base-model gradients in one shared datastore. \textbf{LESS} is our per-PEFT implementation of gradient-influence selection~\cite{xia2024less}. It warms up each target adapter, builds a target-specific Adam-preconditioned gradient datastore, and ranks examples by sketch influence. PCU-Select uses its default conditional scorer, uncertainty penalty, and adaptive quotas.

\subsection{PCU-Select Matches Per-PEFT LESS}

\input{tables/table_main_results}

PCU-Select averages 35.18, compared with 32.29 for Random, 34.44 for RDS+, 34.68 for Influence, and 35.14 for LESS. Across 20 PEFT$\times$task cells, PCU-Select gains 0.74 points over RDS+ and wins 17 cells. Its 95\% fixed-state interval is $[+0.38,+1.06]$. This interval resamples the evaluated cells while keeping the selector, scorer, sketch, and pool fixed. Against Influence, PCU-Select gains 0.50 points, with interval $[+0.21,+0.75]$ and 18 wins. Its 0.04-point gap to LESS has interval $[-0.26,+0.33]$ and 10 wins. Resampling separately within each task yields $[-0.15,+0.22]$. These intervals describe variation across the evaluated cells; they do not include uncertainty from retraining the complete selection pipeline.

The LESS comparison varies by task. PCU-Select gains on MMLU, stays within seed dispersion on GSM8K and HumanEval, and trails on TyDiQA and MLP-only LoRA. Appendix Table~\ref{tab:per-task-compact} reports the per-task view. \textbf{Takeaway.} Reusable supervision improves on PEFT-agnostic selection while preserving the average quality of per-PEFT LESS.

\subsection{Amortization Cuts Marginal Cost by 44$\times$}
\label{sec:reuse}

\input{tables/table_quality_cost_headline}

Registry benefit depends on cost as well as quality. Table~\ref{tab:quality-cost-headline} therefore separates the two cost axes that a registry pays: a \emph{fixed} cost once and a \emph{marginal} cost for each new PEFT. PCU-Select and per-PEFT LESS are the only methods that preserve gradient-selection quality, averaging 35.18 and 35.14. They pay for that quality on different axes. LESS has no fixed cost, but every configuration incurs 63.2 GPU-hours to rebuild a target-specific datastore. PCU-Select spends 144.0 GPU-hours once on reusable supervision. Each new four-task PEFT then costs 1.44 GPU-hours, \textbf{44$\times$ below LESS's marginal cost}.

The marginal axis determines how cost grows with the registry. Adding a task to an existing PEFT costs both selectors one ranking pass: 0.36 GPU-hours for PCU-Select and 0.30 for LESS. Adding a PEFT, however, forces LESS to rebuild its datastore while PCU-Select reuses the offline scorer (Appendix Table~\ref{tab:cost-axes}). The amortization is therefore cross-PEFT, not cross-task: new configurations drive the cost difference.

The cheap reuse shortcut sacrifices quality. Reusing one LESS subset across all five targets (\textbf{Reuse-one-LESS}) costs 63.2 GPU-hours but averages 34.24, below PEFT-agnostic RDS+ at 34.44. A subset optimized for one trainable subspace mismatches the others and discards the condition that made it valuable. PCU-Select instead produces a distinct subset for each target and retains LESS-level average quality.

Equation~\eqref{eq:cost} gives a break-even point of $P^\star=144.0/[62.0+4(0.30-0.36)]=2.33$ configurations. Beyond it, PCU-Select costs less than LESS, and each added configuration widens the gap. Serving the five-PEFT registry costs 151.2 GPU-hours with PCU-Select and 316.0 with LESS, a $2.09\times$ reduction. The unseen-configuration study optionally uses 500 reduced calibration labels from one warm anchor and one update step. This procedure costs 1.05 GPU-hours per $(p,t)$, one quarter of the $\approx4.2$ GPU-hours required by the full label routine. It shifts the worst-case break-even point to 2.50 configurations. Prefix/P-Tuning cannot use this path because they lack native calibration labels. We exclude the shared 12.8 GPU-hour downstream run from every selector.

\textbf{Takeaway.} PCU-Select occupies the quality-preserving amortized point. PEFT-agnostic selectors remain cheaper when users accept a small quality loss. When the registry requires LESS-level quality, PCU-Select onboards each new configuration at $44\times$ lower cost.

The main results establish the quality--cost trade-off. We next isolate why conditioning changes the selected subsets, which components matter, and where transfer fails.
